### 2017-09-07 Graduate - Introduction to Analysis I/Assignment 2/2_Homework20170831.tex
update

\textbf{Solution:}
\bigskip

>>>>

\textbf{Solution:}
\begin{proof}
Let $\{A_k\}_{k=1}^\infty$ be a set of disjoint measurable sets. Denote $B_k = \bigcup_{i=1}^k A_i$, then $\{B_k\}$ is an ascending sequence of measurable sets, and 
$$
m(B_k) = \sum_{i=1}^k m(A_i).
$$
According to the continuity of measure, 
$$
m\left(\bigcup_{k=1}^{\infty}A_k \right) = m\left(\bigcup_{k=1}^\infty B_k\right) = \lim_{k\to\infty}m(B_k) = \lim_{k\to\infty}\sum_{n=1}^n m(A_k) = \sum_{k=1}^{\infty}m(A_k).
$$
It shows the countable additivity of measure.
\end{proof}
\bigskip
